Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-08-19 template.tex
updates on energy derivation

\item Equations \ref{eq:uncert}-\ref{eq:a_err} are used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy.  For Eq. \ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.  We do not compute $\Delta\theta$ from a single string

@@

>>>>

@@

\item Equations \ref{eq:uncert}-\ref{eq:a_err} may be used to reconstruct the natural logarithm of the UHE-$\nu$ cascade energy, $\ln\Lambda$.  For Eq. \ref{eq:uncert}, $\sigma_t$ is measured from the optimized analytic envelope, $c$ and $\theta_{\rm C}$ are known constants, and an assumption must be made for $\Delta\theta$.  We will make the assumption that $\Delta\theta \approx \Delta\theta_{\rm rms}$.  Relying on a single string of RF channels makes calculating $\Delta\theta$ difficult, and geometric event reconstruction usually requires interferometry with multiple strings (cite).  However, the assumption is justified since the $\Delta\theta$ distribution is Gaussian.  The MC truth for $\Delta\theta$ in this analysis is shown in Fig. \ref{fig:fig5}, with a Gaussian fit ($\mu=55.6$ deg, $\sigma=5.77$ deg).  The rms and the $\sigma$ parameter are identical for Gaussian distributions, so we assume $\Delta\theta \approx 5.77$ deg.  The fractional error $\sigma_{\Delta\theta}/\Delta\theta$ is then set to 1.0, reflecting our uncertainty in this parameter.  Solving Eq. \ref{eq:uncert} for $a$ gives

\begin{equation}
a = \frac{c\sigma_t}{\Delta\theta_{\rm rms} \sin\theta_{\rm C}}
\end{equation}

The result for the fractional error in $a$ is found by propagating error from $\sigma_t$ and $\Delta\theta$, defined as $\epsilon$ and $\sigma_{\Delta\theta}$, respectively.  The result is

\begin{equation}
\frac{\sigma_a}{a} = \left(\left(\frac{\epsilon}{\sigma_t}\right)^2 +  \left(\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right)^2\right)^{1/2}
\end{equation}

The first term is small compared to the second, as it is limited by the scan resolution for $\sigma_t$ in the optimization of the analytic envelope and the number of samples per envelope.  The scan resolution is set to 50 ps in the optimization, and there are typically $>10$ samples per envelope.  Thus, the main source of error is $\sigma_{\Delta\theta}$, and

\begin{equation}
\frac{\sigma_a}{a} = \left|\frac{\sigma_{\Delta\theta}}{\Delta\theta}\right| = \left|\frac{\Delta\theta_{\rm rms}}{\Delta\theta_{\rm rms}}\right|\approx 1
\end{equation}

Setting the ratio to 1 reflects the idea that the rms is equal to $\sigma$ for a normal distribution.  Inserting this assumption into Eq. \ref{eq:a_err} gives

\begin{equation}
\frac{\sigma_{\ln\Lambda}}{\ln\Lambda} \approx 2 \label{eq:a_err_2}
\end{equation}

Using Eqs. \ref{eq:em} and \ref{eq:had}, the logarithm of the energy is

\begin{equation}
\ln\Lambda = \left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
\end{equation}

The constants $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively, using Eqs. 10 and 12 from HH (\cite{PhysRevD.105.123019}), at FWHM for the high-energy cascades ($R=0.5$).  Using Eq. \ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ CSWs may be used to deduce the UHE-$\nu$ energy distribution.
